\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Justin van den Anker, Wouter Volders, Hidde Bolijn, Martijn de Lange}
\title{Concept Survival Game}
\begin{document}
\maketitle
\newpage
\section{setting}
The general idea behind this idea is to make people work together in a stressfull enviroment. The game would take place from the inside of a vehicle. The players will reside in this vehicle and are expected to fend off oncoming attackers. Each player has it's own responsibilities in the truck. There are three unique roles for players. First there is the driver, this person is responsible for moving the vehicle through the field of oncoming attackers and making sure to keep the damage done to the vehicle to a minimum. The second role is that of the spotter, this person is in charge of a flashlight to spot oncoming attackers coming from the sides and back of the vehicle and inform the rest of the team of the location of such attackers. The last role in the vehicle is that of the gunner. This person is responsible for shooting the attackers and making sure that the oncoming attackers are shot down and do not damage the vehicle. The game is over when the vehicle is damaged too much and the attackers can get to you. 

\section{Issues}

There might be issues encountered when it comes to the synchronizing of the frame rate of the multiple projectors. This problem might possibly be solved by using the beams of the vehicle as edges of the screen to prevent screen tearing. Another issue might be using the controller for the screens in Unity. There might be the need to write scripts so that Unity understands the input of the controls. The last issue that lies ahead is the synchronizing of the game logic, this has to happen in such a manner that every screen is updated real time so that there is no delay when the driver changes the direction of the vehicle. The screens have to move all at the same time, otherwise there would be a gigantic distortion in the movement of the screens. This problem might have to be solved by using the master computer as a director for the game logic.

\end{document}