\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\author{Justin van den Anker}
\title{Brain Models Mixed Reality Lab}
\begin{document}
\maketitle

\section{Introduction}
As of yet I have had no experience with working in the lab, so I can not compare each model based on compatibility with the lab, nor how well the models will look on the screens. I will however compare these models based on textures and functionality.

\section{3d Brain Medically Accurate Brain Anatomy Model High Resolution}

This design has been made by TurboSquid and has the lowest cost of all models, only 49 dollars. The price however also gives away the quality. The texture definition is low and it does not offer proper quality to show off the capabilities of the lab. The textures are very rough and not very detailed and the colors are also very basic. For 49 dollars it is exactly what you expect to receive.

\url{http://www.turbosquid.com/FullPreview/Index.cfm/ID/921061}

\section{Human Brain Ultimate}
This design looks quite good for 149 dollars, even though the textures are not quite representing the reality, the structure of the brains looks quite well. I think this model would be a good example for a reasonable price.

\url{http://www.turbosquid.com/3d-models/human-brain-3d-model/624395}

\section{3D Human Brain}
This brains look quite well and also represents the brain texture and color closely to reality. The model is also very well detailed and would look rather nicely when looking at it in exploded view. For this model anything under 700 dollars would be a good price, anything above this might not be worth the money.

\url{https://www.zygote.com/poly-models/featured-products/3d-human-brain}

\section{https://www.zygote.com/cad-models/featured-products/solid-3d-human-brain}

This product is simply overpriced for the little extra functionality it might add. The very few differences that might exist between this model and the other models are not worth the substantial amount of money.

\url{https://www.zygote.com/cad-models/featured-products/solid-3d-human-brain}

\section{Human Brain 3D Model}
The price of this model has been set quite high, but it offers a lot. The textures are very well defined and would look nice when they are seen from exploded view. I think this model also offers the most when considering the different systems in the brain and the way they can be viewed individually.

\url{http://www.3dscience.com/3D_Models/Human_Anatomy/Brain/Human_Brain_3D_Model.php}

\section{Conclusion}
My preference would go out to the last model: The Human Brain 3 Model by 3dscience.com. Keep in mind that this advice is based on the textures that can be viewed from the website and not how well they would look in the lab, since I have no technical experience with the lab so far. For the technical details it might be better to ask someone that has worked with these models in a similar setup.
\end{document}