\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Justin van den Anker, Wouter Volders, Hidde Bolijn, Martijn de Lange}
\title{Issue List}
\begin{document}
\maketitle
\section{Synchronizing}
Can Unity synchronize the frame rate on all four walls with the current setup of four slaves and one master computer? Is this supported? If not, would it be possible to write this and how much work would this be?

\section{Sensor Support}
Is it possible to use the controllers that are currently used in the augmented reality lab in Unity? If not, can this be built and how much work would this be?

\section{Player Tracking}
Would it be possible to use the delivered equipment for the augmented reality lab in Unity or is implementation required?


\section{Multiplayer Support Casanova}
Is it achievable to synchronize the game logic over the network simply using casanova or does the game logic need its own multiplayer implementation?

\section{Uniqueness Concept}
How unique is the concept of a survival game and has it not already been made for an augmented reality lab?
\\

Answer: As far a research has shown there is not yet a survival game made for this setup that was made for the same purpose as the concept for the augmented reality lab. The concept of creating a survival game that requires co-op interaction between the players within an augmented reality lab has as of yet not been realized.

\end{document}
